--- 
title: "Free and Open Source Software for Landscape History"
author: "David Lovelace and Robin Lovelace"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The required packages can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("remotes")
```

```{r, include=FALSE}
remotes::install_cran("bookdown")
remotes::install_github("mtennekes/tmap")
```


Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

Reproducible maps can be included, e.g. as follows (source: this [repo](https://github.com/katyrobin/tithe-map-tiles) and this issue):

```{r, warning=FALSE, eval=FALSE}
library(tmap)
tmap_mode("view")
pt = "https://katyrobin.github.io/tithe-map-tiles/hereford-many/{z}/{x}/{y}.png"
h = osmdata::getbb("hereford, uk", format_out = "sf_polygon")
m = tm_basemap(leaflet::providers$OpenStreetMap) +
  tm_tiles(pt, tms = TRUE) +
  tm_shape(h) +
  tm_borders() +
  tm_view(set.view = c(
    sf::st_coordinates(sf::st_centroid(h))[1] + 0.004,
    sf::st_coordinates(sf::st_centroid(h))[2],
    16
  ))
```

```{r, echo=FALSE, eval=FALSE}
tmap_save(m, "m.html")
m = tm_basemap(leaflet::providers$OpenStreetMap) +
  tm_tiles(pt, tms = TRUE) +
  tm_shape(h) +
  tm_borders() +
  tm_view(set.view = c(
    sf::st_coordinates(sf::st_centroid(h))[1] + 0.004,
    sf::st_coordinates(sf::st_centroid(h))[2],
    16
  ))
```


<iframe id="serviceFrameSend" src="m.html" width="100%" height="400"  frameborder="0">